Work Fragmentation in Developer Interaction Data

### 2016-04-19 paper_2.tex
Changes in the discussion

Perhaps the most important thresholds are the inactive time thresholds that delimit interruptions: a \emph{short interruption} is detected after an inactivity of 3 minutes, while a \emph{long interruption} is detected after 12 minutes. Both values come from the literature. More specifically, the work of Gonzalez and Mark \cite{GM04} found that interruptions lasted around 3 minutes, in a field study, and the agree with Kaptelinin and Nardi \cite{KaptelininN07} that interruptions of more than 12 minutes were more likely to correspond to switching activity on a different project or topic.

>>>>

Perhaps the most important thresholds are the inactive time thresholds that delimit interruptions: a \emph{short interruption} is detected after an inactivity of 3 minutes, while a \emph{long interruption} is detected after 12 minutes. Both values come from the literature. More specifically, the work of Gonzalez and Mark \cite{GM04} derived from a field study that interruptions lasted around 3 minutes and mainly correspond to changes at the level of actions; they also found that interruptions of more than 12 minutes were more likely to correspond to switching activity on a different project or topic. Their distinction between actions and activity follows the characterization of work by Activity Theory as presented by Kaptelinin and Nardi \cite{KaptelininN07}.
